%-------------------------
% Resume in Latex
% Author : Brandon Parker
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{hyperref}
\input{glyphtounicode}
\usepackage{xifthen}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% Define custom colors
\definecolor{primary}{RGB}{26,117,155}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingCondensed}[2]{
  \item
    {\small \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Brandon Parker} \\ \vspace{2pt}
    \small \href{mailto:bparkerproductions@gmail.com}{\textcolor{primary}{bparkerproductions@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/bparkerproductions/}{\textcolor{primary}{Linked In}} $|$
    \href{https://github.com/bparkerproductions}{\textcolor{primary}{Github}} $|$
    \href{https://bparkerproductions.com/}{\textcolor{primary}{Portfolio}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Vue.js Frontend Engineer}{August 2021 -- September 2022}
    {Mobile Tool Network}{Remote}
    \resumeSubheadingCondensed{Develop and maintain the startup's front-end Vue.js interface.}{}
    \resumeItemListStart
      \resumeItem{Utilize Vue.js styled components to streamline an outdated admin interface to improve order management and chart key sales data, leading to a 15\% increase in sales revenue.}
      \resumeItem{Use fetch to query Laravel API data through inertia.js to build an interactive order history table that aesthetically displays relevant sales data, increasing order follow-through rate by over 7\%}
    \resumeItemListEnd

    \resumeSubheading
      {Frontend Engineer}{June 2020 -- August 2021}
      {Ethode LLC}{Remote}
      \resumeSubheadingCondensed{Assist and complete several high-impact projects for the agency's biggest clients.}{}
      \resumeItemListStart
        \resumeItem{Quickly contribute to projects that require learning new tech such as Laravel and dotCMS to build and deliver solutions for multi-million-dollar clients.}
        \resumeItem{Refactor jQuery code to ES6 JavaScript for a multi-tenant Laravel app to improve code maintainability and increase front-end performance by over 15\%.}
        \resumeItem{Learn the MVC pattern so I can contribute back-end code to help the team hit critical and time sensitive deadlines.}
    \resumeItemListEnd

    \resumeSubheading
      {PHP Developer}{August 2018 -- September 2020}
      {Lead With Digital LLC}{Remote, Part Time }
      \resumeSubheadingCondensed{Assist and complete several high-impact projects for the agency's biggest clients.}{}
      \resumeItemListStart
        \resumeItem{Quickly contribute to projects that require learning new tech such as Laravel and dotCMS to build and deliver solutions for multi-million-dollar clients.}
        \resumeItem{Refactor jQuery code to ES6 JavaScript for a multi-tenant Laravel app to improve code maintainability and increase front-end performance by over 15\%.}
        \resumeItem{Learn the MVC pattern so I can contribute back-end code to help the team hit critical and time sensitive deadlines.}
    \resumeItemListEnd

    \resumeSubheading
      {Vue.js Developer}{Sept 2018 -- Jan 2020}
      {Fixd Repair}{Remote}
      \resumeSubheadingCondensed{Join this startup's team to build and maintain a brand new Vue.js/Nuxt web app.}{}
      \resumeItemListStart
        \resumeItem{Take an outdated WordPress site and build a new MVP with a tight 2 month deadline using Vue.js, vuex, and vue router.}
        \resumeItem{Use Vue.js, SCSS, and keyframes to develop an interactive location map that increases user engagement and retention.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf {\href{https://github.com/bparkerproductions/Breathr}{\textcolor{primary}{Breathr}}} $|$ \emph{JavaScript, React.js, Redux, Laravel, SASS}}{March 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Using industry best practices, securely authenticate and manage multiple app users and their data.}
            \resumeItem{Use Redux to handle front end state of user actions, the video player, and toggleable components.}
            \resumeItem{Completely redesign Breathr from the ground up using MUI Joy, Tailwind, and the Material UI React component library.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, PHP, SQL (MySQL), HTML/CSS, Java, Python} \\
     \textbf{Frameworks}{: React.js, Vue.js, Laravel, WordPress, Node.js, Spring Boot, Bootstrap} \\
     \textbf{Developer Tools}{: Git, NPM, Yarn, Webpack, Docker} \\
     \textbf{Deployment}{: Ubuntu, Bash, Vagrant, Github, Gitlab } \\
    }}
 \end{itemize}

 %-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Western Governers University}{Millcreek, Utah}
    {Bachelor of Science in  Software Engineering}{December 2023}\vspace{5pt}
  \resumeSubheadingCondensed
    {\href{https://api.badgr.io/public/assertions/vaoUfjA0RT6cZ6-0HZxO3w}{\textcolor{primary}{WGU Capstone Excellence Award}}}{Issued December 2023}
  \resumeSubheadingCondensed
    {\href{https://www.credly.com/badges/a5febee5-016a-4ce3-a014-b824422519a3/public_url}{\textcolor{primary}{AWS Cloud Practitioner Certificate}}}{Issued June 2023}
  \resumeSubheadingCondensed
    {\href{https://www.peoplecert.org/for-corporations/certificate-verification-service}{\textcolor{primary}{ITIL Foundation Certificate in IT Service Management \#GR671528690BP}}}{Issued June 2023}
    
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}